quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-09 paper-quollr.Rmd
Completed the workflow

```{r, echo=TRUE}
# df_bin_centroids <- df_bin_centroids |>
#   dplyr::filter(bin_counts > 10)

@@

```{r, echo=TRUE, eval=knitr::is_html_output()}
# trimesh <- trimesh |>
#   dplyr::filter(bin_counts > 10)

>>>>

```{r, echo=TRUE}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(bin_counts > 10)

@@

```{r, echo=TRUE, eval=knitr::is_html_output()}
trimesh <- trimesh |>
  dplyr::filter(from_count > 10,
                to_count > 10)

trimesh <- update_trimesh_index(trimesh)

### 2025-05-09 paper-quollr.tex
Added hexagonal grid with the notifications
Completed the workflow

#>  1    50    65 0.275   0.127  0.233 0.199          65       67
#>  2    64    65 0.150   0.199  0.233 0.199          39       67
#>  3    64    79 0.150   0.199  0.191 0.271          39       62
#>  4    78    94 0.108   0.271  0.150 0.343          62       34
#>  5    78    79 0.108   0.271  0.191 0.271          62       62
#>  6    21    36 0.358  -0.0171 0.316 0.0550         12       42
#>  7    93    94 0.0665  0.343  0.150 0.343          45       34
#>  8    79    80 0.191   0.271  0.275 0.271          62       68
#>  9    65    66 0.233   0.199  0.316 0.199          67       56
#> 10    66    80 0.316   0.199  0.275 0.271          56       68

@@

@@

\begin{verbatim}
# df_bin_centroids <- df_bin_centroids |>
#   dplyr::filter(bin_counts > 10)

@@

\begin{verbatim}
#> # A tibble: 5,142 x 8
#>         x1    x2    x3         x4        x5       x6        x7 type 
#>      <dbl> <dbl> <dbl>      <dbl>     <dbl>    <dbl>     <dbl> <chr>
#>  1 -0.992   1.91 1.11  -0.000427   0.000624  0.00749  0.00105  model
#>  2 -0.906   1.93 1.41  -0.0000183  0.00331  -0.0204  -0.000363 model
#>  3 -0.680   1.93 1.72  -0.000810  -0.00259  -0.00449  0.00153  model
#>  4 -0.272   1.93 1.96   0.00251    0.00668  -0.0460   0.00128  model
#>  5  0.0760  1.93 2.00   0.00876    0.00447   0.00851 -0.00195  model
#>  6  0.461   1.93 1.89  -0.00478    0.00492   0.00835  0.00172  model
#>  7  0.719   1.99 1.70   0.0109    -0.00349  -0.0297  -0.00223  model
#>  8 -0.985   1.75 0.853 -0.00202    0.000397  0.00331  0.000338 model
#>  9 -0.980   1.66 1.17  -0.000374  -0.00154   0.0165   0.000126 model
#> 10 -0.821   1.64 1.56  -0.000459   0.000538 -0.0123   0.000780 model
#> # i 5,132 more rows
\end{verbatim}

\begin{verbatim}
# trimesh <- trimesh |>
#   dplyr::filter(bin_counts > 10)

>>>>

#>  1    16    26 0.275   0.127  0.233 0.199          65       67
#>  2    25    26 0.150   0.199  0.233 0.199          39       67
#>  3    25    37 0.150   0.199  0.191 0.271          39       62
#>  4    36    49 0.108   0.271  0.150 0.343          62       34
#>  5    36    37 0.108   0.271  0.191 0.271          62       62
#>  6     1     7 0.358  -0.0171 0.316 0.0550         12       42
#>  7    48    49 0.0665  0.343  0.150 0.343          45       34
#>  8    37    38 0.191   0.271  0.275 0.271          62       68
#>  9    26    27 0.233   0.199  0.316 0.199          67       56
#> 10    27    38 0.316   0.199  0.275 0.271          56       68

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/fig-hex-param-1} \caption{The components of the hexagon grid illustrating notation.}\label{fig:fig-hex-param}
\end{figure}

@@

\begin{verbatim}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(bin_counts > 10)

@@

\begin{verbatim}
#> # A tibble: 5,122 x 8
#>         x1    x2    x3         x4        x5       x6        x7 type 
#>      <dbl> <dbl> <dbl>      <dbl>     <dbl>    <dbl>     <dbl> <chr>
#>  1 -0.992   1.91 1.11  -0.000427   0.000624  0.00749  0.00105  model
#>  2 -0.906   1.93 1.41  -0.0000183  0.00331  -0.0204  -0.000363 model
#>  3 -0.680   1.93 1.72  -0.000810  -0.00259  -0.00449  0.00153  model
#>  4  0.461   1.93 1.89  -0.00478    0.00492   0.00835  0.00172  model
#>  5 -0.985   1.75 0.853 -0.00202    0.000397  0.00331  0.000338 model
#>  6 -0.980   1.66 1.17  -0.000374  -0.00154   0.0165   0.000126 model
#>  7 -0.821   1.64 1.56  -0.000459   0.000538 -0.0123   0.000780 model
#>  8 -0.484   1.68 1.87   0.00313    0.00241   0.00823 -0.00117  model
#>  9 -0.0991  1.70 1.99   0.00103    0.00150   0.00877 -0.000193 model
#> 10  0.295   1.74 1.95  -0.00165    0.000459  0.00330  0.000257 model
#> # i 5,112 more rows
\end{verbatim}

\begin{verbatim}
trimesh <- trimesh |>
  dplyr::filter(from_count > 10,
                to_count > 10)

trimesh <- update_trimesh_index(trimesh)
